Consider adding subtasks to more user stories, or remove from existing.

Write about release preparation and release party somewhere (But where?)

Some sort of wrap-up of our process, how we improved through the sprints (see retrospectives) and what we learned from it.

What should be included in the scrum section? (See notes from vejledermødeX).
- Description of scrum in general.
- Description of how we used scrum.

- Write about the fact that we have a lot of internal communication because we always sit together in the group room. No need for standup to know what everyone is working on	and to track progress. (Scrum section)

- Maybe write something about how in the beginning we had meetings with the entire giraf team, and it was impossible to reach consensus and took a long time. (only process group made decisions about process, only PO group made decisions about product)

General notes:
- Interesting things from working in a multi project setting.
- Interesting problems that arose in the multi project setting and how we dealt with them.
- What did we learn. (communication is key)
- Expects at least some code examples in the report, not as much as for example 3rd semester, but there should be something.
- Always good to have examples of "we did this, it was bad because xxx".
- Documentation of all standup meetings should be gathered in one section, in the process part at the end of the report, instead of several across the report. (not necessarily a chapter on standups, the point is that each one shouldn't be described all over the place)

