\section{Sprint Goals}
\label{sect:sprintGoals2}
\subsubsection{Overall Sprint Goals}
Since the first sprint started on re-writing the entire application in Flutter, sprint two focused on getting a release of the core functionality of the weekplanner application. This means that the overall goal of the 2nd sprint was to be close to the level of functionality the Xamarin application had before the move to Flutter. The goals for development where functionality, stability and usability. 

\subsubsection{Our Sprint Goals}
In the second sprint, a lot of time was used to finish and refactor the choose citizen user story from sprint 1. On top of this we worked with the following user stories and tasks:

\begin{itemize}
    \item User story 83: Load configuration from configuration file.
    \item Task 1: Making the process of logging in as a developer less tedious, with a feature to fill in login information automatically.
    \item Task 2: API should time out after a while to prevent requests from crashing the API. 
    \item User story 47: As a guardian I would like to be able to choose a citizen so that I can choose who I’m editing the week plan for.
    \subitem Continuing the integration of the choose citizen screen.
    \item User story 48: As a guardian I would like to be able to log into the system using a username and password, so that I can see my associated citizens.
    \subitem Continuing the development of the loading spinner.
    \item User story 88: As a developer I would like a notification widget so that I avoid duplicated code.
\end{itemize}