\section{Communication}
\label{sect:communication}
Communication between groups played an important role in the product development of the GIRAF project, both for organising and coordinating the workflow, and for groups to support each other during problem solving. Several factors played a part in ensuring good communication.

\begin{itemize}
\item Online communication was done through the use of the chatting features of \textbf{Slack}. Each development group and skill group had their own chat room, making it easy to come in contact with specific groups, for example when one group's issue was dependent on an issue from another group.
Additionally, there was a general room for communication with all groups and an announcement room for important information.
There was also a GitHub watch room, where all updates on issues and pull requests were automatically listed.

\item \textbf{Google Calendar} was used to keep track of meetings held within the GIRAF project, including time and location. This included sprint reviews, sprint retrospectives, sprint planning/introduction, release preparation, standup meetings, and skill group meetings. 

\item 1-3 times a week, \textbf{standup meetings} were used to synchronise information between development groups, keeping track of what each group was currently working on, how work was progressing and whether anyone had problems they needed help with. The meetings could also help discover dependencies between issues from different groups, which they could then figure out how to handle.

\item The \textbf{skill group meetings} were held to share knowledge about front end, back end and server between development groups. They were also used when making more impactful decisions regarding these three areas of the project. 

\item Lastly, the development process made use of \textbf{colocation}. Almost all development groups worked in the group rooms, which were all located near each other. This allowed anyone with a question to simply go ask someone directly. It also made it possible to solve dependencies and conflicts, since people could sit down together and work it out. People from different groups with experience in a certain field could also sit together and work on specific problems. 
\end{itemize}