\section{Sprint Goals}
\subsubsection{Overall Sprint Goals} \label{sect:1SprintGoals}
During the first sprint, there was a shift in goals. Initially, both user stories with new functionality and user stories with improvements on existing functionality were included. These were based on remaining user stories from the previous year. Later on in the sprint, the goals shifted to focus on stability and usability, as described in section~\ref{sect:ProjectGoals}.
Soon after, it was decided that application development should be done in Flutter instead of Xamarin, which meant that the entire front-end had to be rewritten in Flutter.
After the core of the application had been translated to Flutter, the goals stabilized into user stories of translation and improvement of stability and usability.


\subsubsection{Our Sprint Goals}
Due to the shift in overall goals throughout the sprint, the user stories we ended up working with also shifted throughout the sprint. Firstly, at the sprint planning meeting, we were assigned the user story of making the Weekplanner application available offline.
After changing focus to stability and usability, we then received a user story of improving the user interface of the choose citizen screen in the Weekplanner application. This was combined with the translation of the choose citizen screen after the decision to switch to Flutter.

Overall, the work covered in this sprint is:

\begin{itemize}
    \item User story 9: As a guardian, I would like that the app is fully available offline so that I can still use it if the internet is down.
    \item User story 6: As a guardian I would like the choose citizen screen to look better so it makes it easier for me to find the correct user.
    \item Adapting to the change from Xamarin to Flutter.
    \item User story 47: As a guardian I would like to be able to choose a citizen so that I can choose who I’m editing the week plan for.
    \item User story 48: As a guardian I would like to be able to log into the system using a username and password, so that I can see my associated citizens.
\end{itemize}

%Overall, based on the user stories we were assigned, we ended up working with the following tasks:
\iffalse
\begin{itemize}
    \item T1: Make the Weekplanner application able to function offline.
    \item T2: Improve the user interface of the choose citizen screen in Xamarin.
    \item T3: Adapting to the change from Xamarin to Flutter.
    \item T4: Design the user interface of the choose citizen screen in Flutter.
    \item T5: Improve the user interface of the login screen. 
\end{itemize}
\fi



