\section{Sprint Review}
\subsubsection{Overall Sprint Review}
%der var et møde hvor alle folk sagde hvad de havde lavehe
According to the process manual, a sprint review should be held like described in section~\ref{sect:Scrum}.
The sprint review was held at the end of sprint 1, where the PO group was present along with one spokesperson from each group. 
Here, every spokesperson informed the other groups about the status of the implementation of the development group's user stories.
The sprint review of the first sprint deviated a bit from how the process manual describes a sprint review. Since the sprint review was held only one week after shifting the application from Xamarin to Flutter, no user stories were fully implemented yet. Because of this, the review did not include the part where the PO group accepts or rejects user stories. This was also the reason behind the decision not to release anything this sprint.
%Opnåede vi sprint goals?(ikke rigtigt, pga. skift til Flutter, men fik forbedret lidt.
%hvad havde vi lavet?

\subsubsection{Our Sprint Review}
During the first week of development using the Flutter framework, we as a group had a total of two user stories. This part of the sprint review will only cover the Flutter user stories, as the Xamarin user stories did not lead to any implementation.
During the first week after the shift to Flutter we made a lot of progress on the UI part of the two user stories. However, some of the tasks where not yet fully implemented. A list of finished and unfinished tasks is shown below.

\subsubsection{Finished}
\begin{itemize}
    \item \textbf{User Story 47: As a guardian I would like to be able to choose a citizen so that I can choose who I’m editing the week plan for.}
    \subitem Make a screen to list all citizens.
    \subitem Make/Use a BLoC to handle the data.
    \subitem Make a widget to standardize how to show a citizen.
    
    \item \textbf{User Story 48: As a guardian I would like to be able to log into the system using a username and password, so that I can see my associated citizens.}
    \subitem Ensure that login works correctly (cannot login with incorrect information).
    \subitem Ensure that login matches prototype and design guide.
\end{itemize}

\subsubsection{Unfinished}
\begin{itemize}
    \item \textbf{User Story 47: As a guardian I would like to be able to choose a citizen so that I can choose who I’m editing the week plan for.}
    \subitem When  choosing  a  citizen  I  should  be  routed  to  the  "Choose  weekplan"  screen.
    \subitem Tests.
    
    \item \textbf{User Story 48: As a guardian I would like to be able to log into the system using a username and password, so that I can see my associated citizens.}
    \subitem A loading spinner should be shown while contacting API, so the user does not think the app is frozen.
    \subitem Tests.
\end{itemize}

Since the user stories are not yet completed, the development will continue in the next sprint. 